---
title: "Football Analysis with R"
author: "Guillermo Vinue"
date: "`r Sys.Date()`" 
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Football Analysis with R}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
  %\VignetteDepends{RcppParallel}
  %\VignetteKeyword{no_install}
---

This document introduces the functions of the **fawir** package for friendly data scraping from PES Master (https://www.pesmaster.com/), creating some visualizations and using a player recruitment algorithm.

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r packages, message=FALSE, eval=FALSE}
# First, load fawir and other packages required:
library(fawir)
library(dplyr)
library(tidyr)
```

## Friendly web scraping

```{r scrape, eval=FALSE}
# Prepare the data with the details needed to scrape:
df_players_links <- data.frame(league = "Premier League",
                               team = "Arsenal",
                               position = "CB",
                               name = "William Saliba",
                               link = "/william-saliba/efootball-2022/player/126689/")

# Prepare the data with the skill definitions:
pes_skills <- data.frame(english = c("Heading", "Weighted Pass", "Man Marking",
                                     "Interception", "Blocker", "Aerial Superiority",
                                     "Acrobatic Clearance"),
                         description = c("Improve the accuracy of headers",
                                         "Apply back-spin when playing lofted passes",
                                         "Stick to chase down an opponent",
                                         "Better interception skills",
                                         "Player’s chances to block passes and shots",
                                         "Player’s chances to win aerial balls",
                                         "Clear the ball even from awkward positions"))

# Prepare the data with the AI playing styles:
pes_ai <- data.frame(english = "Long Ball Expert",
                     description = "A player who frequently plays the long ball")

url_player <- df_players_links %>% pull(link)

url_pes_base <- "https://www.pesmaster.com"
analyst_name <- "Guillermo Vinue"

data_pes <- do_scrape_pesmaster(url_player, url_pes_base, df_players_links,
                                pes_skills, pes_ai, analyst_name, TRUE)
```

## Visualization

1. Explore leagues and playing styles:

```{r visualize1, eval=FALSE}
do_explore_leagues(pesmaster_sample)
do_explore_playing_styles(pesmaster_sample)
```

2. Explore player profiles:

```{r visualize2, eval=FALSE}
# Prepare the data with the abilities related to each position:
pesmaster_pos_abi <- data.frame(type = rep("Goalkeeper", 6),
                                ability = c("goalkeeping", "gk_awareness", "gk_catching",
                                            "gk_parrying", "gk_reflexes", "gk_reach" ))

pesmaster_algorithm <- do_prepare_profiles(pesmaster_sample, 
                                           pesmaster_playing_styles, 
                                           pesmaster_pos_abi)                                             
                                             
do_explore_profiles(pesmaster_algorithm, "Goalkeeper")
```

3. Explore texts:

```{r visualize3, eval=FALSE}
mystopwords <- tibble(word = c("goalkeeper", "goalkeepers", "player", "ball", "frequently"))
do_explore_texts(pesmaster_sample, pesmaster_positions, mystopwords)
```

## Recruitment

```{r recruitment, eval=FALSE}
# Prepare the scouting report:
df0 <- pesmaster_sample %>%
  select(-skills, -playing_style_ai) %>%
  unite("scouting_report", c(characteristics, skills_descr, 
                             playing_style_ai_descr), sep = ", ") %>%
  mutate(scouting_report = gsub(", NA", "", scouting_report))

# Define the type of player to search for:
query <- "A predatory striker, attacking of 80, kicking power of 72, dribbling of 67"

# Run the algorithm:
res <- do_player_recruitment(df0, 50, 5, 10, 0.5, 3, TRUE, query)
res %>% select(league, team, name, position)
```

## Definition of playing styles

```{r playing styles, eval=FALSE}
# Prepare the data with the abilities related to each position:
pesmaster_pos_abi <- data.frame(type = rep("Goalkeeper", 6),
                                ability = c("goalkeeping", "gk_awareness", "gk_catching", 
                                            "gk_parrying", "gk_reflexes", "gk_reach" ))
                                             
pesmaster_algorithm <- do_prepare_profiles(pesmaster_sample, 
                                           pesmaster_playing_styles, 
                                           pesmaster_pos_abi)
 
do_check_def_playing_styles(pesmaster_playing_styles, pesmaster_sample, pesmaster_algorithm, 
                            c("Defensive Goalkeeper", "Offensive Goalkeeper"), 50, 5, 10, 
                            0.5, 10, TRUE, TRUE)
```

### Information about the session

```{r session info}
sessionInfo()
```
